---
title: "Untitled"
author: "Koki Ando"
date: "5/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Prep

```{r}
library(tidyverse)
library(naniar)
library(simputation)
test = read.csv("test.csv")
train = read.csv("train.csv")

# Combining datasets
test$SalePrice = 0
train$Train = "YES"
test$Train = "NO"
merged_dat = rbind(train, test)
```

# NA First Check

```{r}
prop_miss(merged_dat)
```



# Understanding variables

+ MSSubClass: The building class
+ MSZoning: The general zoning classification
+ LotFrontage: Linear feet of street connected to property
+ LotArea: Lot size in square feet
+ Street: Type of road access
+ Alley: Type of alley access
+ LotShape: General shape of property
+ LandContour: Flatness of the property
+ Utilities: Type of utilities available
+ LotConfig: Lot configuration
+ LandSlope: Slope of property
+ Neighborhood: Physical locations within Ames city limits
+ Condition1: Proximity to main road or railroad
+ Condition2: Proximity to main road or railroad (if a second is present)
+ BldgType: Type of dwelling
+ HouseStyle: Style of dwelling
+ OverallQual: Overall material and finish quality
+ OverallCond: Overall condition rating
+ YearBuilt: Original construction date
+ YearRemodAdd: Remodel date
+ RoofStyle: Type of roof
+ RoofMatl: Roof material
+ Exterior1st: Exterior covering on house
+ Exterior2nd: Exterior covering on house (if more than one material)
+ MasVnrType: Masonry veneer type
+ MasVnrArea: Masonry veneer area in square feet
+ ExterQual: Exterior material quality
+ ExterCond: Present condition of the material on the exterior
+ Foundation: Type of foundation
+ BsmtQual: Height of the basement
+ BsmtCond: General condition of the basement
+ BsmtExposure: Walkout or garden level basement walls
+ BsmtFinType1: Quality of basement finished area
+ BsmtFinSF1: Type 1 finished square feet
+ BsmtFinType2: Quality of second finished area (if present)
+ BsmtFinSF2: Type 2 finished square feet
+ BsmtUnfSF: Unfinished square feet of basement area
+ TotalBsmtSF: Total square feet of basement area
+ Heating: Type of heating
+ HeatingQC: Heating quality and condition
+ CentralAir: Central air conditioning
+ Electrical: Electrical system
+ 1stFlrSF: First Floor square feet
+ 2ndFlrSF: Second floor square feet
+ LowQualFinSF: Low quality finished square feet (all floors)
+ GrLivArea: Above grade (ground) living area square feet
+ BsmtFullBath: Basement full bathrooms
+ BsmtHalfBath: Basement half bathrooms
+ FullBath: Full bathrooms above grade
+ HalfBath: Half baths above grade
+ Bedroom: Number of bedrooms above basement level
+ Kitchen: Number of kitchens
+ KitchenQual: Kitchen quality
+ TotRmsAbvGrd: Total rooms above grade (does not include bathrooms)
+ Functional: Home functionality rating
+ Fireplaces: Number of fireplaces
+ FireplaceQu: Fireplace quality
+ GarageType: Garage location
+ GarageYrBlt: Year garage was built
+ GarageFinish: Interior finish of the garage
+ GarageCars: Size of garage in car capacity
+ GarageArea: Size of garage in square feet
+ GarageQual: Garage quality
+ GarageCond: Garage condition
+ PavedDrive: Paved driveway
+ WoodDeckSF: Wood deck area in square feet
+ OpenPorchSF: Open porch area in square feet
+ EnclosedPorch: Enclosed porch area in square feet
+ 3SsnPorch: Three season porch area in square feet
+ ScreenPorch: Screen porch area in square feet
+ PoolArea: Pool area in square feet
+ PoolQC: Pool quality
+ Fence: Fence quality
+ MiscFeature: Miscellaneous feature not covered in other categories
+ MiscVal: $Value of miscellaneous feature
+ MoSold: Month Sold
+ YrSold: Year Sold
+ SaleType: Type of sale
+ SaleCondition: Condition of sale


# Imputation

```{r}
vars = c("MSZoning", "Utilities", "BsmtFullBath", "BsmtHalfBath", "Functional", "Exterior1st", "Exterior2nd", 
         "BsmtFinSF1", "BsmtFinSF2", "BsmtUnfSF", "TotalBsmtSF", "Electrical", "KitchenQual", "GarageCars", "GarageArea", "SaleType")
vars_int = c("BsmtFullBath", "BsmtHalfBath", "BsmtFinSF1", "BsmtFinSF2", "BsmtUnfSF", "TotalBsmtSF", "GarageCars", "GarageArea")
vars_factor = c("MSZoning", "Utilities", "Functional", "Exterior1st", "Exterior2nd", "Electrical", "KitchenQual", "SaleType")
```

```{r}
merged_dat = impute_mean_at(merged_dat, vars_int)
merged_dat = merged_dat %>% 
  impute_cart(MSZoning ~ .) %>% 
  impute_cart(Utilities ~ .) %>% 
  impute_cart(Functional ~ .) %>% 
  impute_cart(Exterior1st ~ .) %>% 
  impute_cart(Exterior2nd ~ .) %>% 
  impute_cart(Electrical ~ .) %>% 
  impute_cart(KitchenQual ~ .) %>% 
  impute_cart(SaleType ~ .)
# lm_imputed_dat = merged_dat
# merged_dat = lm_imputed_dat
```

## Mode Imputation

```{r}
# Pool Quality
merged_dat$PoolQC = as.character(merged_dat$PoolQC)
merged_dat[is.na(merged_dat$PoolQC),]$PoolQC = "None"
merged_dat$PoolQC = factor(merged_dat$PoolQC)

merged_dat$MiscFeature = as.character(merged_dat$MiscFeature)
merged_dat[is.na(merged_dat$MiscFeature),]$MiscFeature = "High"
merged_dat$MiscFeature = factor(merged_dat$MiscFeature)

merged_dat$Alley = as.character(merged_dat$Alley)
merged_dat[is.na(merged_dat$Alley),]$Alley = "HighSP"
merged_dat$Alley = factor(merged_dat$Alley)

merged_dat$Fence = as.character(merged_dat$Fence)
merged_dat[is.na(merged_dat$Fence),]$Fence = "Hig"
merged_dat$Fence = factor(merged_dat$Fence)

merged_dat$FireplaceQu = as.character(merged_dat$FireplaceQu)
merged_dat[is.na(merged_dat$FireplaceQu),]$FireplaceQu = "Hg"
merged_dat$FireplaceQu = factor(merged_dat$FireplaceQu)

merged_dat = impute_lm(merged_dat, GarageYrBlt ~ SalePrice)

# GarageType table(merged_dat$GarageType)
merged_dat$GarageType = as.character(merged_dat$GarageType)
merged_dat[is.na(merged_dat$GarageType),]$GarageType = "None"
merged_dat$GarageType = factor(merged_dat$GarageType)
merged_dat$GarageQual = as.character(merged_dat$GarageQual)
merged_dat[is.na(merged_dat$GarageQual),]$GarageQual = "No"
merged_dat$GarageQual = factor(merged_dat$GarageQual)

merged_dat$GarageCond = as.character(merged_dat$GarageCond)
merged_dat[is.na(merged_dat$GarageCond),]$GarageCond = "No"
merged_dat$GarageCond = factor(merged_dat$GarageCond)
merged_dat$GarageFinish = as.character(merged_dat$GarageFinish)
merged_dat[is.na(merged_dat$GarageFinish),]$GarageFinish = "No"
merged_dat$GarageFinish = factor(merged_dat$GarageFinish)


merged_dat[is.na(merged_dat$BsmtFinType1),]$BsmtFinType1 = "GLQ"
merged_dat[is.na(merged_dat$BsmtFinType2),]$BsmtFinType2 = "Unf"
merged_dat[is.na(merged_dat$BsmtCond),]$BsmtCond = "TA"
merged_dat[is.na(merged_dat$BsmtExposure),]$BsmtExposure = "No"
merged_dat[is.na(merged_dat$BsmtQual),]$BsmtQual = "TA"

merged_dat[is.na(merged_dat$MasVnrType), ]$MasVnrType = "None"
merged_dat[is.na(merged_dat$MasVnrArea), ]$MasVnrArea = 0

merged_dat[is.na(merged_dat$LotFrontage), ]$LotFrontage = 0
```

## NA Check

```{r}
prop_miss(merged_dat)
```

# Feature Engineering

## Year related

### YearBuilt (Original Construction Date) & YearRemodAdd :(Remodel date (same as construction date if no remodeling or additions))

YearBuildCategory: 

+ New: 2000~2015
+ Middle: 1980 ~ 2000
+ Old: ~1980

```{r}
merged_dat = merged_dat %>% 
  mutate(YearBuiltCategory = case_when(
    YearRemodAdd >= 2000 & YearRemodAdd < 2015 ~ "New",
    YearRemodAdd >= 1980 & YearRemodAdd < 2000 ~ "Middle",
    YearRemodAdd < 1980 ~ "Old"))
```

## Sale

### SaleType: Type of sale

"WD"
+ WD 	Warranty Deed - Conventional 不動産権譲渡
+ CWD	Warranty Deed - Cash 不動産権譲渡
+ VWD	Warranty Deed - VA Loan 不動産権譲渡
"NEW"
+ New	Home just constructed and sold

+ COD	Court Officer Deed/Estate 不動産権譲渡

"ConLow"
+ Con	Contract 15% Down payment regular terms
+ ConLI	Contract Low Interest

+ ConLw	Contract Low Down payment and low interest

+ ConLD	Contract Low Down

"Oth"
+ Oth	Other

```{r}
merged_dat = merged_dat %>% 
  mutate(SaleCategory = case_when(
    SaleType %in% c("WD", "CWD", "VWD") ~ "WD",
    SaleType %in% c("Con", "ConLI") ~ "ConLow",
    TRUE ~ as.character(SaleType)
  ))
```

### SaleCondition: Condition of sale

+ Normal	Normal Sale
+ Abnorml	Abnormal Sale -  trade, foreclosure, short sale
+ AdjLand	Adjoining Land Purchase
+ Alloca	Allocation - two linked properties with separate deeds, typically condo with a garage unit	
+ Family	Sale between family members
+ Partial	Home was not completed when last assessed (associated with New Homes)

```{r}
merged_dat %>% 
  group_by(SaleCondition) %>%
  summarise(ave = mean(SalePrice))
```

## WoodDeckSF: Wood deck area in square feet

+ VeryLarge: 500~
+ Large: 400~500
+ Middle: 150~400
+ Narrow: 50~150
+ Tiny: 1~50
+ None: 0

```{r}
merged_dat = merged_dat %>% 
  mutate(WoodDeckArea = case_when(
    WoodDeckSF >= 500 ~ "VeryLarge",
    WoodDeckSF >= 400 & WoodDeckSF < 500 ~ "Large",
    WoodDeckSF >= 150 & WoodDeckSF < 400 ~ "Middle",
    WoodDeckSF >= 50 & WoodDeckSF < 150 ~ "Narrow",
    WoodDeckSF > 0 & WoodDeckSF < 50 ~ "Tiny",
    WoodDeckSF == 0 ~ "None"
  ))
```

## Pool

### PoolQC: Pool quality
		
+ Ex	Excellent
+ Gd	Good
+ TA	Average/Typical
+ Fa	Fair
+ NA	No Pool

```{r}
merged_dat = merged_dat %>% 
  mutate(HasPool = ifelse(PoolQC == "None", 0, 1))
```

## Garage

### GarageType

```{r}
merged_dat = merged_dat %>% 
  mutate(HasGarage = ifelse(GarageType == "None", 0, 1))
```


```{r}
merged_dat$GarageType %>% table
```


```{r}
merged_dat %>% 
  select(contains("Garage")) %>% head
```


