---
title: "house"
author: "Koki Ando"
date: "5/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


[House Price Prediction](https://www.kaggle.com/c/house-prices-advanced-regression-techniques/data)

```{r}
library(tidyverse)
test = read.csv("test.csv")
train = read.csv("train.csv")
```

# EDA

```{r}
dim(train)
```

## Summary of train

```{r}
# summary(train)
```

## Sale Price

```{r}
train %>% 
  ggplot(aes(SalePrice)) +
  geom_histogram(bins = 50)
```

```{r}
summary(train$SalePrice)
```

## Missing values

```{r}
apply(train, 2, prop_miss)
```


### Dealing with Missing values

#### Combine datasets

```{r}
test$SalePrice = 0
train$Train = "YES"
test$Train = "NO"
merged_dat = rbind(train, test)
```

#### Check NAs again

```{r}
prop_miss(merged_dat)
```

```{r}
library(naniar)
library(simputation)
sort(apply(merged_dat, 2, n_miss), decreasing = T)
```

```{r}
merged_dat %>% 
  miss_var_summary() %>%
  filter(n_miss >= 1 & n_miss < 5) %>% 
  filter(variable %in% vars)
```

```{r}
vars = c("MSZoning", "Utilities", "BsmtFullBath", "BsmtHalfBath", "Functional", "Exterior1st", "Exterior2nd", 
         "BsmtFinSF1", "BsmtFinSF2", "BsmtUnfSF", "TotalBsmtSF", "Electrical", "KitchenQual", "GarageCars", "GarageArea", "SaleType")
```

```{r}
merged_dat %>% 
  select(vars) %>% 
  str()
```

```{r}
vars_int = c("BsmtFullBath", "BsmtHalfBath", "BsmtFinSF1", "BsmtFinSF2", "BsmtUnfSF", "TotalBsmtSF", "GarageCars", "GarageArea")
vars_factor = c("MSZoning", "Utilities", "Functional", "Exterior1st", "Exterior2nd", "Electrical", "KitchenQual", "SaleType")
merged_dat = impute_mean_at(merged_dat, vars_int)
merged_dat %>% 
  impute_cart(MSZoning ~ .)
```

# Check NAs

```{r}
miss_var_summary(merged_dat) 
```



## Top 3 missing values

```{r}
prop_miss(merged_dat$PoolQC)
prop_miss(merged_dat$MiscFeature)
prop_miss(merged_dat$Alley)
```

It seems that vast majority of PoolQC, MiscFeature and Alley columns data is missing. In this case, I am not going to use these variables.

```{r}
merged_dat = select(merged_dat, -PoolQC, -MiscFeature, -Alley)
```



!!!!!後ほど試すこと
これらの数値はそもそも、欠損値であるか無いかが重要かもしれない。そこを後ほど試す！


```{r}
prop_miss(merged_dat)
```

```{r}
library(naniar)
miss_var_summary(merged_dat)
apply(merged_dat, 2, n_miss)
apply(merged_dat, 2, prop_miss)
```


#### Fence

```{r}
merged_dat %>% 
  ggplot(aes(Fence)) +
  geom_bar(stat = "count")
```

Should I use this data set?......


```{r}
md.pairs(merged_dat)$mm
```


#### Imputation

```{r}
Mode = function(x){
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}
```



# Baseline prediction

```{r}
train = merged_dat %>% 
  filter(Train == "YES") %>% 
  select(-Train)
test = merged_dat %>% 
  filter(Train == "NO") %>% 
  select(-Train, -SalePrice)
```



```{r}
library(rpart)
library(randomForest)
model_rpart = rpart(data = train, SalePrice ~ .)
# model_rf = randomForest(SalePrice ~ ., data = train,
#                         ntree = 500, importance = TRUE)


test$SalePrice = predict(model_rf, test)
submission = select(test, Id, SalePrice)
write.csv(submission, "submission.csv", row.names = FALSE)
```

